---
title: "GLAir"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(GLAir)
```


This package provides tools to download air quality data for London.

## Installation

To install GLAir from github you need to use the `devtools` package.

If you do not have `devtools` installed, you will need to run the commented out line of code as well.


```{r Installation, eval=FALSE}
#install.packages("devtools")
#devtools::install_github("LiRogers/GLAir")
```

## Package functions

GLAir contains functions that fetch meta data and monitoring data for air quality monitoring sites across the whole of London, or for the 2 main sensor networks, the London Air Quality Network (LAQN) and the Air Quality England (AQE) network.

### Site meta data

Meta data can be fetched as follows:


```{r, warning=FALSE}
meta_data <- getMetaAllLondon()

meta_data %>%
  head()
```

This gets meta data for all air quality monitoring sites across London. The equivalent functions for the 2 networks are `getMetaLAQN()` and `getMetaAQE()`.

### Monitoring data

Hourly monitoring data can be fetched as follows:

```{r, warning=FALSE}
# For all sites and species:
df <- importAllLondon(start_date = as.Date('2019-01-01'),
                      end_date = as.Date('2019-01-07'))

# For specified sites and species:
df <- importAllLondon(start_date = as.Date('2019-01-01'),
                      end_date = as.Date('2019-01-07'),
                      sites = c("BG1", "WL1", "MY1"),
                      species = c("NO2", "PM10", "PM25"))

# Providing meta data - this will speed up your code if you're making multiple calls to importAllLondon
meta_data <- getMetaAllLondon()
df <- importAllLondon(start_date = as.Date('2019-01-01'),
                      end_date = as.Date('2019-01-07'),
                      sites = c("BG1", "WL1", "MY1"),
                      species = c("NO2", "PM10", "PM25"),
                      meta_data = meta_data)

df %>% 
  head()
```

This will work for sites in both networks. To fetch the data from just one of the networks the equivalent functions are `importLAQN()` and `importAQE()`, which have the same parameters as `importAllLondon()`.

The format of the monitoring data returned will work with the utility functions included in the [OpenAir R package](http://davidcarslaw.github.io/openair/).